### 2015-05-13 background.tex
update to change sections to S symbol

Example~\ref{fig:data_race_example} presents multiple data races that \whoop automatically found in the generic\_nvram Linux char driver (see Section~\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can read/write access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order resulting into nondeterministic behavior.

>>>>

Example~\ref{fig:data_race_example} presents multiple data races that \whoop automatically found in the generic\_nvram Linux char driver (see \S\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can read/write access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order resulting into nondeterministic behavior.

### 2015-05-13 evaluation.tex
update to change sections to S symbol

We performed experiments to validate the usefulness of the \whoop approach (Section~\ref{whoop}) and its combination with \corral (Section~\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel distribution.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate race-checking with \corral.

@@

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we are just checking the specific pair and are not accounting for the effect of other threads (see Section~\ref{corral}); this can also cause \corral to miss some races.

@@

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a context-switch bound (csb) of 2, 5 and 9, respectively. For standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).

>>>>

We performed experiments to validate the usefulness of the \whoop approach (\S\ref{whoop}) and its combination with \corral (\S\ref{corral}). We first present race-checking results from running \whoop and \corral on \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel distribution.\footnote{\url{https://www.kernel.org}} We then evaluate the runtime performance and scalability of \corral and \whoop + \corral with different yield instrumentation granularities and context-switch bounds.
Our results demonstrate that \whoop can efficiently accelerate race-checking with \corral.

@@

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analyzing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we are just checking the specific pair and are not accounting for the effect of other threads (see \S\ref{corral}); this can also cause \corral to miss some races.

@@

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was configured with a time budget of 10 hours (T.O. denotes timeout) and a context-switch bound (csb) of 2, 5 and 9, respectively. For standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see \S\ref{corral}). The table also shows the number of context-switches per instrumentation (\#Y).
